BVP Paper

### 2017-12-07 tex/bvp_paper.tex
somes changes to paper & code

\section{Introduction}
\label{sec:intro}
In many simple studies of convection, the choice of boundary conditions greatly influences the dynamics
of the evolved state.  In studies of incompressible, Boussinesq, \RB convection (RBC), many studies
employ fixed temperature (Dirichlet) boundary conditions at the top and bottom, or fixed heat flux
(Neumann) boundary conditions at both plates.  The former case represents plates of infinite conductivity,
whereas the latter plates of finite conductivity.  In both cases, the choice of symmetric boundary
conditions maintains overall system symettry, and both have been shown to transport heat in nearly the
same manner \cite{johnston&doering2009}.

Studies of convection in stratified systems which aim to model convection in natural, astrophysical systems,
such as that in the outer envelope of low-to-moderate mass stars like the Sun, often employ a mixture of these
two types of boundary conditions (references, references).  The flux at the lower boundary is fixed, modeling
the constant energy generation of the stellar core, while the outer boundary condition is held at a fixed temperature,
effectively allowing all heat generated to escape.

>>>>

\section{Introduction}
\label{sec:intro}
In numerical studies of convection, the chosen boundary conditions at the upper and lower plates
determines key quantities of the dynamics of the evolved state.
Studies of incompressible, Boussinesq, \RB convection (RBC) often
employ fixed temperature (Dirichlet) or fixed heat flux
(Neumann) boundary conditions at both plates.  
Dirichlet conditions represent plates of infinite conductivity,
whereas Neumann condition model plates of finite conductivity.  
In both cases, choosing symmetric boundary conditions maintains overall system symmetry, 
and despite evolving towards quite different thermal structures, both types of conditions
transport heat in the same manner \cite{johnston&doering2009}.

Studies of convection in stratified systems which aim to model convection 
in astrophysical systems, such as the outer envelopes of low-to-moderate mass stars 
like the Sun, often employ a mixture of these
two types of boundary conditions \cite{hurlburt&all1984, cattaneo&all1991}.  
The flux at the lower boundary is fixed, modeling
the constant energy generation of the stellar core, 
while the outer boundary condition is held at a fixed temperature,
modeling the surface of a star which must output the energy generated internally.
